---
title: "Variable 1"
author: "Sami Hlebak"
date: "Monday, November 02, 2015"
output: html_document
---

This is code is used to calculate variable 1A.
Packages in use:
```{r}
library(xlsx)
```
Here are the parameters:
```{r}
SWDC<-4.54*10^(-7)#from xlsx Parameters&Results $O$17
                  #Derived conversion coefficent
                  #solid wood products carbon factor
                  #average life time
PPHL<-2.53#from xlsx Parameters&Results $P$10
          #Paper products decay rate (half-life)
PPCF<-3.90*10^(-7)#from xlsx Parameters&Results $0$18
                  #Paper products carbon factor
                  #Average lifetime
                  #derived conversion coefficent
VIBY<-0.08#from xlsx swcalc b979
          #tells the values lost when placed in use
          #same for all
IPY<-0.01#percent increase per year from base year
        #from xlsx swcalc b980
        #same for all

```


The code here calculates the percent of carbon lost when the product is placed in use.
```{r}
#LPIU= Lost when placed in use
#VIBY= value in base year
swcalc= read.xlsx("swcalc.xlsx",1,header = F)
i=0
for (i in 1900:2050){
  LPIU= VIBY+(i-2000)(IPY)
  print(i)
} 
```

The code here will calculate the amount of carbon remaining in use in various end uses by year (million tonnes)
```{r}
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use
for (i in ){
  ACR=#year iexp(-ln(2)/(FIND URL)(year i-(1900-1)(1-LPIU)))
}
```

The code here calculates the total carbon stored per year.
```{r}
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use
for (i in ){
  #sum(ACRi:ACRi-1,na.rm)
}
```

This code calculates the carbon in solid wood for year i - the carbon in solid wood in year i-1
```{r}
#CCSW=Carbon in solid wood
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use

```

This code will calculate the stock change of carbon in metric tons
```{r}
#SEMT=stock exchange metric tons
#CCSW=Carbon in solid wood
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use

```