---
title: "Variable 1"
author: "Sami Hlebak"
date: "Monday, November 02, 2015"
output: html_document
---

This is code is used to calculate variable 1.

The code here calculates the percent of carbon lost when the product is placed in use.
```{r}
#LPIU= Lost when placed in use
for (i in 1900:2050){
  LPIU= #value in base year+(year i-2000)(% increase per year from base)
} 
```

The code here will calculate the amount of carbon remaining in use in various end uses by year (million tonnes)
```{r}
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use
for (i in ){
  ACR=#year iexp(-ln(2)/(FIND URL)(year i-(1900-1)(1-LPIU)))
}
```

The code here calculates the total carbon stored per year.
```{r}
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use
for (i in ){
  #sum(ACRi:ACRi-1,na.rm)
}
```

This code calculates the carbon in solid wood for year i - the carbon in solid wood in year i-1
```{r}
#CCSW=Carbon in solid wood
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use

```

This code will calculate the stock change of carbon in metric tons
```{r}
#SEMT=stock exchange metric tons
#CCSW=Carbon in solid wood
#CPY=carbon per year
#ACR=Amount of carbon remaining
#LPIU= Lost when placed in use

```